The problem and promise of scale in multilayer animal social networks

### 2020-05-25 paper/manuscript-trad.Rmd
fst trad

Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Multilayer networks
provide a way to bridge these different scales to examine social
phenotypes in more holistic ways rather than looking at each scale separately as
has traditionally been done. From a monolayer network perspective, social
phenotypes are increasingly linked to important fitness for individuals of
various species, including primates [@Brent_2017; @Thompson_2019], dolphins
[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
social scales, types of interactions, and temporal, seasons and stages of life,
have emerged as important for understanding fitness consequences in the context
of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011].

@@

## Movement ecology and collective movement

@@

## Habitat selection and space use
Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality across scales.

>>>>

<!-- fitness -->
Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Multilayer networks
provide a way to bridge these different scales to examine social
phenotypes in more holistic ways rather than looking at each scale separately as
has traditionally been done. From a monolayer network perspective, social
phenotypes are increasingly linked to important fitness for individuals of
various species, including primates [@Brent_2017; @Thompson_2019], dolphins
[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
social scales, types of interactions, and temporal, seasons and stages of life,
have emerged as important for understanding fitness consequences in the context
of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011].

@@

@@

<!-- ## Habitat selection and space use -->
Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality across scales.
